On the Cram\'{e}r-Rao bound for polynomial phase signals

### 2013-03-28 paper.tex
fixed refs

Polynomial-phase signals have applications including radar, sonar, biology, and radio communication~\cite{Angeby_estimating_2000,Levanon_Radar_signals_2004}.  %The signals are also used to describe the sounds emitted by bats for echo-location \cite{Peleg_DPT_1995,Moss_2005echolocation,Suga_1975_bats_echolocation}.  
Of practical importance is the estimation of the coefficients $\beta = (\beta_0, \dots \beta_m)\in\reals^{m+1}$ from $N$ consecutive samples $y_1, \dots, y_N$ where 
\begin{equation}\label{eq:yndatamodel}
y_n = s_n(\beta) + w_n
\end{equation}
and $\{w_n, n \in \ints\}$ is a sequence of noise variables.  Many estimators have been studied and implemented~\cite{Angeby_estimating_2000,Oshea_cpf_2004,Morelande_bayes_unwrapping_2009_tsp,Kitchen_polyphase_unwrapping_1994,Peleg_DPT_1995, Djuric_phase_unwrap_chirp_1990}.

@@

\section{Conclusion}

Using a family of discrete orthogonal polynomials we describe closed form formulae for the Cram\'{e}r-Rao lower bounds for unbiased estimators of polynomial phase signals.

@@

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Angeby_estimating_2000}
J.~\"Angeby, Estimating signal parameters using the nonlinear instantaneous
  least squares approach, IEEE Trans. Sig. Process. 48 (2000) 2721--2732.

\bibitem{Levanon_Radar_signals_2004}
N.~Levanon, E.~Mozeson, Radar Signals, John Wiley \& Sons, 2004.

\bibitem{Oshea_cpf_2004}
P.~O'Shea, A fast algorithm for estimating the parameters of a quadratic {FM}
  signal, IEEE Trans. Sig. Process. 52~(2) (2004) 385 -- 393.

\bibitem{Morelande_bayes_unwrapping_2009_tsp}
M.~Morelande, Parameter estimation of phase-modulated signals using {Bayesian}
  unwrapping, IEEE Trans. Sig. Process. 57~(11) (2009) 4209--4219.

\bibitem{Kitchen_polyphase_unwrapping_1994}
J.~Kitchen, A method for estimating the coefficients of a polynomial phase
  signal, Signal Processing 37~(1) (1994) 463--470.

\bibitem{Peleg_DPT_1995}
S.~Peleg, B.~Friedlander, The discrete polynomial-phase transform, IEEE Trans.
  Sig. Process. 43~(8) (1995) 1901--1914.

\bibitem{Djuric_phase_unwrap_chirp_1990}
P.~M. Djuric, S.~M. Kay, Parameter estimation of chirp signals, IEEE Trans.
  Acoust. Speech Signal Process. 38~(12) (1990) 2118--2126.

\bibitem{Peleg1991_CRB_PPS_1991}
S.~Peleg, B.~Porat, The {Cram\'{e}r-Rao} lower bound for signals with constant
  amplitude and polynomial phase, IEEE Trans. Sig. Process. 39~(3) (1991)
  749--752.

\bibitem{Kay1993_stat_sig_est_theory}
S.~M. Kay, Fundamentals of Statistical Signal Processing: Estimation Theory,
  Prentice-Hall, 1993.

\bibitem{Bjork_num_methods_least_square_1996}
A.~B\"{j}orck, Numerical Methods for Least Squares Problems, SIAM, 1996.

\bibitem{Chebyshev_discrete_polys1864}
P.~Chebyshev, Sur l'interpolation, Zapiski Akademii Nauk 1~(4) (1864) 539--560.

\bibitem{Gram_discrete_polys1883}
J.~P. Gram, {\"{U}ber die Entwicklung reeller Funktionen in Reihen mittels der
  Methode der kleinsten Quadrate}, Journal f\"{u}r die reine und angewandte
  Mathematik 94 (1883) 41--73.

\bibitem{Eisinberg2007_discerete_otho_poly_equidist}
A.~Eisinberg, G.~Fedele, Discrete orthogonal polynomials on equidistant nodes,
  International Mathematical Forum 2~(21) (2007) 1007--1020.

\bibitem{Abramowitz_Stegen_stirling_numbers_1972}
M.~Abramowitz, I.~A. Stegun, Stirling Numbers of the First Kind, 9th Edition,
  Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical
  Tables, Dover, 1972.

\bibitem{McKilliam2010thesis}
R.~G. McKilliam, Lattice theory, circular statistics and polynomial phase
  signals, Ph.D. thesis, University of Queensland, Australia (December 2010).

\bibitem{McKilliam2009IndentifiabliltyAliasingPolyphase}
R.~G. McKilliam, I.~V.~L. Clarkson, Identifiability and aliasing in
  polynomial-phase signals, IEEE Trans. Sig. Process. 57~(11) (2009)
  4554--4557.

>>>>

Polynomial-phase signals have applications including radar, sonar, biology, and radio communication~\cite{Angeby_estimating_2000}.  %The signals are also used to describe the sounds emitted by bats for echo-location \cite{Peleg_DPT_1995,Moss_2005echolocation,Suga_1975_bats_echolocation}.  
Of practical importance is the estimation of the coefficients $\beta = (\beta_0, \dots \beta_m)\in\reals^{m+1}$ from $N$ consecutive samples $y_1, \dots, y_N$ where 
\begin{equation}\label{eq:yndatamodel}
y_n = s_n(\beta) + w_n
\end{equation}
and $\{w_n, n \in \ints\}$ is a sequence of noise variables.  Many estimators have been studied and implemented~\cite{Angeby_estimating_2000,Oshea_cpf_2004,Morelande_bayes_unwrapping_2009_tsp,Peleg_DPT_1995, Djuric_phase_unwrap_chirp_1990}.

@@

\section{Conclusion}
%\vspace{-0.2cm}
Using a family of discrete orthogonal polynomials we describe closed form formulae for the Cram\'{e}r-Rao lower bounds for unbiased estimators of polynomial phase signals.

@@

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi
%\vspace{-0.2cm}
\bibitem{Angeby_estimating_2000}
J.~\"Angeby, Estimating signal parameters using the nonlinear instantaneous
  least squares approach, IEEE Trans. Sig. Process. 48 (2000) 2721--2732.
%\vspace{-0.1cm}
%\bibitem{Levanon_Radar_signals_2004}
%N.~Levanon, E.~Mozeson, Radar Signals, John Wiley \& Sons, 2004.
%\vspace{-0.1cm}
\bibitem{Oshea_cpf_2004}
P.~O'Shea, A fast algorithm for estimating the parameters of a quadratic {FM}
  signal, IEEE Trans. Sig. Process. 52~(2) (2004) 385 -- 393.
%\vspace{-0.1cm}
\bibitem{Morelande_bayes_unwrapping_2009_tsp}
M.~Morelande, Parameter estimation of phase-modulated signals using {Bayesian}
  unwrapping, IEEE Trans. Sig. Process. 57~(11) (2009) 4209--4219.
%\vspace{-0.1cm}
%\bibitem{Kitchen_polyphase_unwrapping_1994}
%J.~Kitchen, A method for estimating the coefficients of a polynomial phase
%  signal, Signal Processing 37~(1) (1994) 463--470.
%\vspace{-0.1cm}
\bibitem{Peleg_DPT_1995}
S.~Peleg, B.~Friedlander, The discrete polynomial-phase transform, IEEE Trans.
  Sig. Process. 43~(8) (1995) 1901--1914.
%\vspace{-0.1cm}
\bibitem{Djuric_phase_unwrap_chirp_1990}
P.~M. Djuric, S.~M. Kay, Parameter estimation of chirp signals, IEEE Trans.
  Acoust. Speech Signal Process. 38~(12) (1990) 2118--2126.
%\vspace{-0.1cm}
\bibitem{Peleg1991_CRB_PPS_1991}
S.~Peleg, B.~Porat, The {Cram\'{e}r-Rao} lower bound for signals with constant
  amplitude and polynomial phase, IEEE Trans. Sig. Process. 39~(3) (1991)
  749--752.
%\vspace{-0.1cm}
\bibitem{Kay1993_stat_sig_est_theory}
S.~M. Kay, Fundamentals of Statistical Signal Processing: Estimation Theory,
  Prentice-Hall, 1993.
%\vspace{-0.1cm}
\bibitem{Bjork_num_methods_least_square_1996}
A.~B\"{j}orck, Numerical Methods for Least Squares Problems, SIAM, 1996.
%\vspace{-0.1cm}
\bibitem{Chebyshev_discrete_polys1864}
P.~Chebyshev, Sur l'interpolation, Zapiski Akademii Nauk 1~(4) (1864) 539--560.
%\vspace{-0.1cm}
\bibitem{Gram_discrete_polys1883}
J.~P. Gram, {\"{U}ber die Entwicklung reeller Funktionen in Reihen mittels der
  Methode der kleinsten Quadrate}, Journal f\"{u}r die reine und angewandte
  Mathematik 94 (1883) 41--73.
%\vspace{-0.1cm}
\bibitem{Eisinberg2007_discerete_otho_poly_equidist}
A.~Eisinberg, G.~Fedele, Discrete orthogonal polynomials on equidistant nodes,
  International Mathematical Forum 2~(21) (2007) 1007--1020.
%\vspace{-0.1cm}
\bibitem{Abramowitz_Stegen_stirling_numbers_1972}
M.~Abramowitz, I.~A. Stegun, Stirling Numbers of the First Kind, 9th Edition,
  Handbook of Mathematical Functions with Formulas, Graphs, and Mathematical
  Tables, Dover, 1972.
%\vspace{-0.1cm}
\bibitem{McKilliam2010thesis}
R.~G. McKilliam, Lattice theory, circular statistics and polynomial phase
  signals, Ph.D. thesis, University of Queensland, Australia (December 2010).
%\vspace{-0.1cm}
\bibitem{McKilliam2009IndentifiabliltyAliasingPolyphase}
R.~G. McKilliam, I.~V.~L. Clarkson, Identifiability and aliasing in
  polynomial-phase signals, IEEE Trans. Sig. Process. 57~(11) (2009)
  4554--4557.
